The zoon R package for reproducible and shareable species distribution modelling

### 2017-01-04 ms.Rmd
Add my affiliation
Sorry, promise I'll have a better look asap. Ddon't let me hold back submission etc.

---
title: "The zoon R package for reproducible and shareable species distribution modelling"
author: 
  - Nick Golding$^1$, Tom August$^2$, Tim C.D. Lucas$^3$, David K. Gavaghan$^4$, Emiel Van Loon$^5$ & Greg McInerny$^6$
  - $^1$ School of BioSciences, University of Melbourne, Parkville VIC, Australia
  - $^2$ [please fill in]
  - $^3$ [please fill in]
  - $^4$ [please fill in]
  - $^5$ [please fill in]
  - $^6$ [please fill in]
bibliography: zoon_app.bib
csl: mee.csl
output:
  pdf_document:
    fig_caption: yes
    includes:
      in_header: latex_preamble.tex
---

>>>>

---
title: "The zoon R package for reproducible and shareable species distribution modelling"
author: 
  - Nick Golding$^1$, Tom August$^2$, Tim C.D. Lucas$^3$, David K. Gavaghan$^4$, Emiel Van Loon$^5$ & Greg McInerny$^6$
  - $^1$ School of BioSciences, University of Melbourne, Parkville VIC, Australia
  - $^2$ [please fill in]
  - $^3$ Oxford Big Data Institute, Li Ka Shing Centre for Health Information and Discovery Nuffield Department of Medicine, University of Oxford, Oxford, U.K.
  - $^4$ [please fill in]
  - $^5$ [please fill in]
  - $^6$ [please fill in]
bibliography: zoon_app.bib
csl: mee.csl
output:
  pdf_document:
    fig_caption: yes
    includes:
      in_header: latex_preamble.tex
---
